|

### 2025-12-01 output/AM_Main.Rmd
Add changes in typesetting proof

Panel (a) of Figure \@ref(fig:item-plot-out) shows
the item representation in the uncorrelated case,
while the $`r CORR_OBL_OUT`$ case is shown in panels (b) to (d)
under different conditions:
with item coordinates computed from the agnostic version of the parameters
(panel (b)), or from the correlation-based version,
either using an appropriate oblique basis (panel (c)),
or plotting them directly in the canonical basis (panel (d)).
Keeping the horizontal axis invariant in panel (c)
allows for a better comparison with the other plots;
therefore, we have chosen a $`r TRANSFORM_MATRIX_TRANSP_INV`$ that
only rotates the vertical axis [@harman_modern_1976]:

@@

Panels (a) and (b) show that,
even if the agnostic coordinates are the same in both cases,
their relative position with respect to the latent trait distribution is not
---this is the effect of disregarding the covariance structure.
The correlation-based coordinates, plotted in panels (c) and (d),
are also different in general from their agnostic counterpart (panel (b)).
Although they do not vary in some cases (items 1 and 4),
the difference is especially salient in the location of items 2 and 3,
which are close to the 90% contour in the agnostic version
but almost on the 50% contour in the correlation-based one.
Panel (d) also illustrates the effect of plotting the coordinates directly
on the canonical basis;
the item locations and their positions relative to the distribution
are correctly represented (which makes comparing with panel (b) easier),
but their discrimination parameters and angles with the axes are distorted:
For example, items 4 and 5 seem to be equally discriminating,
when Table \@ref(tab:example-items-table-out) panel (c) show they are not;
and item 1 forms 45-degree angles with both axes,
instead of the 30-degree ones shown in Table \@ref(tab:example-items-table-out).

>>>>

Panel (a) of Figure \@ref(fig:item-plot-out) shows
the item representation in the uncorrelated case,
while the $`r CORR_OBL_OUT`$ case is shown in panels (b) to (d)
under different conditions:
with item coordinates computed from the agnostic version of the parameters
(panel [b]), or from the correlation-based version,
either using an appropriate oblique basis (panel [c]),
or plotting them directly in the canonical basis (panel [d]).
Keeping the horizontal axis invariant in panel (c)
allows for a better comparison with the other plots;
therefore, we have chosen a $`r TRANSFORM_MATRIX_TRANSP_INV`$ that
only rotates the vertical axis [@harman_modern_1976]:

@@

Panels (a) and (b) show that,
even if the agnostic coordinates are the same in both cases,
their relative position with respect to the latent trait distribution is not
---this is the effect of disregarding the covariance structure.
The correlation-based coordinates, plotted in panels (c) and (d),
are also different in general from their agnostic counterpart (panel [b]).
Although they do not vary in some cases (items 1 and 4),
the difference is especially salient in the location of items 2 and 3,
which are close to the 90% contour in the agnostic version
but almost on the 50% contour in the correlation-based one.
Panel (d) also illustrates the effect of plotting the coordinates directly
on the canonical basis;
the item locations and their positions relative to the distribution
are correctly represented (which makes comparing with panel [b] easier),
but their discrimination parameters and angles with the axes are distorted.
For example, items 4 and 5 seem to be equally discriminating,
when Table \@ref(tab:example-items-table-out) panel (c) show they are not;
and item 1 forms 45-degree angles with both axes,
instead of the 30-degree ones shown in Table \@ref(tab:example-items-table-out).
